\\textsc{Mathematical Description}

### 2022-06-27 100-math-description/GR-sslcm-math-description.Rmd
Disable the repeat_header_continued kable feature
This causes a bug where the last line of the TeX is duplicated and printed as output at the bottom of the table. A kableExtra bug.

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = symbol_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "25px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "50px") %>%
  column_spec(4, width = "300px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

@@

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = param_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "65px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "290px") %>%
  row_spec(1:(nrow(tab)-1), hline_after = TRUE) %>%
  footnote(number = footnote_key, number_title = "Prior Distributions:", title_format = c("italic", "underline"), escape = FALSE, threeparttable = TRUE)
```

@@

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = data_tab_cap, escape = FALSE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD")) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "70px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "295px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

@@

kable(tab[,2:4], "latex", booktabs = TRUE, linesep = "", caption = equation_tab_cap, escape = FALSE, longtable = TRUE, align = "lrl") %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header"), repeat_header_continued = "\\textit{(Continued on next page...)}") %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Generic", min(which(tab$Phase == 0)), max(which(tab$Phase == 0)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "55px") %>%
  column_spec(2, width = "15px") %>%
  column_spec(3, width = "365px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major")
```

>>>>

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = symbol_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "25px") %>%
  column_spec(2, width = "50px") %>%
  column_spec(3, width = "50px") %>%
  column_spec(4, width = "300px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

@@

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = param_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "65px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "290px") %>%
  row_spec(1:(nrow(tab)-1), hline_after = TRUE) %>%
  footnote(number = footnote_key, number_title = "Prior Distributions:", title_format = c("italic", "underline"), escape = FALSE, threeparttable = TRUE)
```

@@

kable(tab[,2:5], "latex", booktabs = TRUE, linesep = "", caption = data_tab_cap, escape = FALSE, longtable = TRUE) %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "50px") %>%
  column_spec(2, width = "70px") %>%
  column_spec(3, width = "20px") %>%
  column_spec(4, width = "295px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "full")
```

@@

kable(tab[,2:4], "latex", booktabs = TRUE, linesep = "", caption = equation_tab_cap, escape = FALSE, longtable = TRUE, align = "lrl") %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD", "repeat_header")
                # repeat_header_continued = "\\textit{(Continued on next page...)}"
                ) %>%
  row_spec(0, bold = TRUE) %>%
  pack_rows("Generic", min(which(tab$Phase == 0)), max(which(tab$Phase == 0)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Juvenile", min(which(tab$Phase == 1)), max(which(tab$Phase == 1)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Ocean Juvenile", min(which(tab$Phase == 2)), max(which(tab$Phase == 2)), bold = TRUE, hline_after = TRUE) %>%
  pack_rows("Freshwater Adult", min(which(tab$Phase == 3)), max(which(tab$Phase == 3)), bold = TRUE, hline_after = TRUE) %>%
  column_spec(1, width = "55px") %>%
  column_spec(2, width = "15px") %>%
  column_spec(3, width = "365px") %>%
  collapse_rows(1, valign = "bottom", latex_hline = "major")
```
